\section{Introduction}\label{sec:introduction}




Spatial and immersive audio techniques have been the beneficiaries of
significant research interest over the past few decades.
Recent developments in virtual and augmented reality technologies and
\textit{object-based} audio~\citep{geier_object-based_2010} have led to an
acceleration in interest in the creation of virtual sound fields via approaches
such as Wave Field Synthesis (WFS) and Higher Order Ambisonics
(HOA)~\citep{berkhout_acoustic_1993,ahrens_theory_2008,daniel_further_2003,
    frank_producing_2015}.
These techniques call for the deployment of large numbers of loudspeakers, and
centralised, \textit{in situ} installations of dedicated hardware and software.
The costs associated with such installations have seen them largely restricted
to the preserve of concert venues, cinemas, and institutions with the means to
purchase and operate large-scale systems of this sort.

Advancements in embedded computing mean that there now exist an assortment of
small, low-cost devices with support for audio digital signal processing (DSP).
These devices are open source, relatively easy to program, and may provide
support for communication over ubiquitous computer networking equipment and
protocols.
A network of such devices could be used to \textit{distribute} the problem of
audio spatialisation, potentially lowering the barrier to entry to what is
otherwise a comparatively exclusive branch of audio research.

In this article \textemdash{} which is adapted from a master's thesis written by
the corresponding author, and builds on previous work on a microcontroller-based
networked audio client~\citep{rushton_microcontroller-based_2023} \textemdash{}
we describe the development of a distributed system for spatial and immersive
audio.

\input{sections/introduction/networked-audio}
\input{sections/introduction/hardware}
\input{sections/introduction/spatial-audio}
\input{sections/introduction/distributed-systems}

\subsection{Objectives and Outlook}\label{subsec:objectives}

The primary focus of this work is an exploration of employing a network of
hardware modules to act as a co-ordinated networked-audio system with a view to
supporting a distributed approach to audio spatialisation techniques.
It is hoped that in selecting a low-cost hardware platform, using ubiquitous
computer networking technologies, and keeping the overall design as simple as
possible, the work here could lead to a lowering of the barrier to entry of
the creation of large scale spatial and immersive audio installations.

WFS was chosen as a target implementation for the comparative ease with which
its algorithm can be parallelised.
Equations~\eqref{eq:driving-signal} and~\eqref{eq:driving-function} illustrate
that the driving signal for a given secondary point source is dependent only
on the signals and relative positions of the virtual primary sources, and is
independent of the driving signals for the other secondary sources.
Subject to the feasibility of delivering the source signals to the hardware
modules, each module would simply have to produce the driving signals for the
two output channels for which it is responsible.
Then the temporal challenges described in \secref{subsec:challenges} would
be the remaining concern: to what extent could synchronicity be maintained
in the absence of a shared, authoritative source of time, and what would the
effects of loss of synchronicity be on the performance of the distributed
algorithm and the integrity of the holophonic effect?

Before beginning work on this project, a distributed WFS system was
developed, based on the Teensy 4.1 microcontroller and JackTrip protocol.
This consisted of an audio application running on a general purpose computer,
delivering audio over JackTrip to a collection of hardware modules, and
WFS control data over multicast UDP.\
Strategies were developed for mitigating the effects of jitter and clock drift,
and these serve as the basis for work on the project described in this article.

The previous system was not formally evaluated, but, anecdotally, provided
support for the holophonic effect of primary-source WFS.\
These initial efforts were based on a limited understanding of the
problem-space, and called for further development.
It was deemed, also, that the implementation was constrained by the more
opinionated aspects of the JackTrip system.
